ShabbyPages: A Reproducible Document Denoising and Binarization Dataset

### 2023-02-11 paper/paper.tex
Minor edits

\begin{figure}
\centering
\includegraphics[width=0.98\columnwidth, frame]{figures/quad.png}
\caption{Sample patches from \emph{ShabbyPages}.} \label{fig1}
\end{figure}

@@

The pipeline uses 23 of the augmentations from \emph{Augraphy}.  Augmentations such as \texttt{"BookBinding"} and \texttt{"Folding"} were excluded since these spatial transformations alter the document image geometry by shifting pixel placement from their original position.  Such transforms would render images unsuitable for supervised training and analysis by many common metrics that rely on pixel-to-pixel comparisons against groundtruths.

\texttt{"PaperFactory"} was used with 300 textures, dramatically increasing the possible variations in the final dataset.

@@

\begin{figure}
\centering
\includegraphics[width=0.98\columnwidth, frame]{figures/shabbyreal_denoising.png}
\caption{Sample \emph{ShabbyReal} images and their Shabby\_NAFNet-denoised versions.}
\label{fig:shabbyreal_denoising}
\end{figure}

>>>>

\begin{figure}
\centering
\includegraphics[width=0.98\columnwidth]{figures/what_causes_corruption.png}
\caption{Sample clean and corresponding dirty patch from \emph{ShabbyPages}.} \label{fig1}
\end{figure}

@@

The pipeline uses 23 of the augmentations from \emph{Augraphy}.  Augmentations such as \texttt{BookBinding} and \texttt{Folding} were excluded since these spatial transformations alter the document image geometry by shifting pixel placement from their original position.  Such transforms would render images unsuitable for supervised training and analysis by many common metrics that rely on pixel-to-pixel comparisons against groundtruths.

\texttt{PaperFactory} was used with 300 textures, dramatically increasing the possible variations in the final dataset.

@@

\begin{figure}
\centering
\includegraphics[width=0.98\columnwidth]{figures/quad.png}
\caption{Sample patches from \emph{ShabbyPages} dataset.}
\label{fig:shabbyreal_denoising}
\end{figure}
